### 2017-02-02 local-capability-machine.tex
added the last region proofs

\begin{lemma}
  \label{lem:hnwl-mono-str}
  $H^\nwl_{\start,\addrend} \; s$ is monotone w.r.t $\futurestr$ for all $s \in \States$ and $\start$ and $\addrend$
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:hnwl-mono-str}]
  Let $\hat{W}' \futurewk \hat{W}$ be given and let 
  \begin{equation}
    \label{pf:hnwl-mono:ass}
    \npair{\ms} \in H^\nwl_{\start,\addrend}\; s \; \hat{W}
  \end{equation}
  and show
  \[
    \npair{\ms} \in H^\nwl_{\start,\addrend}\; s \; \hat{W}'
  \]
  From \ref{pf:hnwl-mono:ass}, we get $\dom(\ms) = [\start,\addrend]$. Now let $\addr \in [\start,\addrend]$ be given and show
  \begin{enumproof}
    \item \nonlocal{\ms(a)} \label{pf:hnwl-mono:ob1}
    \item $\npair[n-1]{\ms(a)} \in \stdvr(\xi(\hat{W}'))$ \label{pf:hnwl-mono:ob2}
  \end{enumproof}
  \ref{pf:hnwl-mono:ob1} follows trivially from \label{pf:hnwl-mono:ass}. \ref{pf:hnwl-mono:ob1} follows from Assumption~\ref{pf:hpwl-mono:ass}, \ref{pf:hnwl-mono:ob1} (which we just argued), $W' \futurestr W$, and Lemma~\ref{lem:stdvr-non-loc-priv-mono}.
\end{proof}

@@

\begin{lemma}
  \label{lem:iotastau-is-a-region}
  $\iota^{\sta,u}(v,\ms)$ is a region for all $v \in \{\perma, \temp\}$ and $\ms$.
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:iotastau-is-a-region}]
  % TODO
\end{proof}

>>>>

\begin{lemma}
  \label{lem:hnwl-mono-str}
  $H^\nwl_{\start,\addrend} \; s$ is monotone w.r.t $\futurestr$ for all $s \in \States$ and $\start$ and $\addrend$
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:hnwl-mono-str}]
  Let $\hat{W}' \futurestr \hat{W}$ be given and let 
  \begin{equation}
    \label{pf:hnwl-mono:ass}
    \npair{\ms} \in H^\nwl_{\start,\addrend}\; s \; \hat{W}
  \end{equation}
  and show
  \[
    \npair{\ms} \in H^\nwl_{\start,\addrend}\; s \; \hat{W}'
  \]
  From \ref{pf:hnwl-mono:ass}, we get $\dom(\ms) = [\start,\addrend]$. Now let $\addr \in [\start,\addrend]$ be given and show
  \begin{enumproof}
    \item \nonlocal{\ms(a)} \label{pf:hnwl-mono:ob1}
    \item $\npair[n-1]{\ms(a)} \in \stdvr(\xi(\hat{W}'))$ \label{pf:hnwl-mono:ob2}
  \end{enumproof}
  \ref{pf:hnwl-mono:ob1} follows trivially from \ref{pf:hnwl-mono:ass}. \ref{pf:hnwl-mono:ob1} follows from Assumption~\ref{pf:hpwl-mono:ass}, \ref{pf:hnwl-mono:ob1} (which we just argued), $\hat{W}' \futurestr \hat{W}$, Theorem~\ref{thm:world-existence}, and Lemma~\ref{lem:stdvr-non-loc-priv-mono}.
\end{proof}

@@

\begin{lemma}
  \label{lem:hstau-mono-str}
  $H^{\sta,u}(\ms) \; s$ is monotone w.r.t $\futurestr$ for all $s \in \States$ and $\ms$.
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:hstau-mono-str}]
  Let $\hat{W}' \futurestr \hat{W}$ be given and let 
  \begin{equation}
    \label{pf:hstau-mono:ass}
    \npair{\ms'} \in H^{\sta,u}(\ms)\; s \; \hat{W}
  \end{equation}
  and show
  \[
    \npair{\ms'} \in H^{\sta,u}(\ms)\; s \; \hat{W}'
  \]
  From \ref{pf:hstau-mono:ass}, we get $\ms' = \ms$. Now let $\addr \in \dom(\ms)$ be given and show
  \begin{enumproof}
    \item \nonlocal{\ms(a)} \label{pf:hstau-mono:ob1}
    \item $\npair[n-1]{\ms(a)} \in \stdvr(\xi(\hat{W}'))$ \label{pf:hstau-mono:ob2}
  \end{enumproof}
  \ref{pf:hstau-mono:ob1} follows trivially from \ref{pf:hstau-mono:ass}. \ref{pf:hstau-mono:ob1} follows from Assumption~\ref{pf:hstau-mono:ass}, \ref{pf:hstau-mono:ob1} (which we just argued), $\hat{W}' \futurestr \hat{W}$, Theorem~\ref{thm:world-existence} and Lemma~\ref{lem:stdvr-non-loc-priv-mono}.
\end{proof}

\begin{lemma}
  \label{lem:iotastau-is-a-region}
  $\iota^{\sta,u}(v,\ms)$ is a region for all $v \in \{\perma, \temp\}$ and $\ms$.
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:iotastau-is-a-region}]
  Follows from Lemma~\ref{lem:hstau-mono-str} and Lemma~\ref{lem:future-pub-impl-future-priv}.
\end{proof}
